Engineering the Servo Web Browser Engine using Rust

### 2015-10-23 icse16-servo/intro.tex

%!TEX root = paper.tex
\section{Introduction}
\label{sec:intro}
The heart of a modern web browser is the browser engine, which is the code responsible
for loading, processing, evaluating, and rendering web content.
There are three major browser engine families:
\begin{enumerate}
\item Trident/Spartan, the engine in Internet Explorer~\cite{IE}
\item Webkit\cite{WEBKIT}/Blink, the engine in Safari~\cite{SAFARI}, Chrome~\cite{CHROME}, and Opera~\cite{OPERA}
\item Gecko, the engine in Firefox~\cite{FIREFOX}
\end{enumerate}
All of these engines have at their core many millions of lines of \Cplusplus{} code.
The use of \Cplusplus{} has enabled all of these browsers to achieve excellent sequential
performance on a single web page, particularly on desktop computers.
But, on mobile devices with lower processor speed but many more processors, these browsers
do not provide the same level of interactivity~\cite{parallelizing-web-pages,ZOOMM}.
Further, in an informal inspection of the critical security bugs in Gecko, we determined that
roughly 50\% of the bugs are use after free, out of range access, or related to integer
overflow.
The other 50\% are split between errors in tracing values from the JavaScript heap in the
\Cplusplus{} code and errors related to dynamically compiled code.

>>>>

%!TEX root = paper.tex
\section{Introduction}
\label{sec:intro}
Modern web browsers do not just display static pages, but run web applications
with complexity similar to native software.
From application suites such as Google Apps\footnote{\url{https://apps.google.com}} to games
based on the Unreal Engine,\footnote{\url{https://www.unrealengine.com/}}
modern browsers are a delivery platform for the types of rich media experiences historically
tied to single hardware and operating system platforms.

The architecture called upon to realize these experiences was not exactly designed for the task.

TODO: history of web in one sentence.

The heart of a modern web browser is its engine, the code responsible
for loading, processing, evaluating, and rendering web content.
There are three major browser engine families:
\begin{enumerate}
\item Trident/Spartan, the engine in Internet Explorer~\cite{IE}
\item Webkit\cite{WEBKIT}/Blink, the engine in Safari~\cite{SAFARI}, Chrome~\cite{CHROME}, and Opera~\cite{OPERA}
\item Gecko, the engine in Firefox~\cite{FIREFOX}
\end{enumerate}
All of these engines have at their core many millions of lines of \Cplusplus{} code.
The use of \Cplusplus{} has enabled all of these browsers to achieve excellent sequential
performance on a single web page, particularly on desktop computers.
But, on mobile devices with lower processor speed but many more processors, these browsers
do not provide the same level of interactivity~\cite{parallelizing-web-pages,ZOOMM}.
Further, in an informal inspection of the critical security bugs in Gecko, we determined that
roughly 50\% of the bugs are use after free, out of range access, or related to integer
overflow.
The other 50\% are split between errors in tracing values from the JavaScript heap in the
\Cplusplus{} code and errors related to dynamically compiled code.
